---
title: "Problem Sets: 2 & 3"
author: "Braulio Güémez"
date: "31/8/2021"
output: html_document
---

# *Problem Set 02*

## Open the libraries and the data

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(readr)

nc <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTm2WZwNBoQdZhMgot7urbtu8eG7tzAq-60ZJsQ_nupykCAcW0OXebVpHksPWyR4x8xJTVQ8KAulAFS/pub?gid=202410847&single=true&output=csv")

```

## Exercise 1

R is considering `habit`to be a character type of variable. `Visits` is considered as a number with decimals type of variable.

## Exercise 2

There is a positive relation between the length of a pregnancy and the birth weight of a baby in pounds. Thus, for every week increase there is a correspondent increase in the weight of the baby.

## Exercise 3

```{r}
nc |> ggplot(aes(weeks, gained)) + geom_point() + labs(x="Length of pregnancy (in weeks)", y="Weight gained during pregnancy", title="Relationship between pregnancy duration and weight gained duing pregnancy")
```

## Exercise 4

A. It colors the points according to the values of the variable `premie`, that indicates whether a birth was early (`premie`) or went full term.

B. Three

C. 36 weeks

## Exercise 5

```{r}
nc |> ggplot(aes(mage,weight, col=factor(gender))) + geom_point() + geom_smooth(method="lm")
```

There seems to be no strong relationship between the mother's age and the weight of her newborn. There is a slight positive slope (blue line) in the case of male newborns but not in the case of female ones.

## Exercise 6

A. The number of births of a single child.

B. 39

C. 1 bin and all the 800 cases would be in that bin

## Exercise 7

```{r}
nc |> ggplot(aes(weight)) + geom_histogram() + labs(x="Weight of the newborn (in lbs)", y="n" , title="Distribution of newborn weights")
```

## Exercise 8

```{r}
nc |> ggplot(aes(weight)) + geom_histogram(binwidth  =0.5) + facet_wrap(.~gender)   
```

Male newborns have a higher average birth weight. This can be seen is the right-skewed distribution of weight in the case of male newborns (Panel 2)

## Exercise 9

```{r}
nc |>  ggplot(aes(mature, gained)) + geom_boxplot() + labs(x="Maturity status of the mothers", y="Weight", title="Weight gained during pregnancy by maturity status of the mothers")
```

The median weight gain during pregnancy is a bit larger in younger moms than older moms

## Exercise 10

```{r}
nc |>  ggplot(aes(habit, weeks)) + geom_boxplot()
```

The duration of the pregnancy varies more for smokers than for non-smokers.

## Exercise 11

```{r}
nc |>  ggplot(aes(fage)) + geom_histogram(binwidth = 3) 
```

The father's age distribution is skewed to the left, that is, younger ages.

## Exercise 12

```{r}
nc |>  ggplot(aes(whitemom, weight)) + geom_boxplot()
```

The median birth weight of babies is higher for white than non-white mothers.

## Exercise 13

```{r}
nc |>  ggplot(aes(mage, weeks)) + geom_point() + geom_smooth(method="lm")
```

There seems to be no significant association between the mother's age and the duration of pregnancy

# *Problem Set 03*

## Open the data (libraries already opened)

```{r message=FALSE, warning=FALSE}
data(txhousing)
glimpse(txhousing)
```

## Question 1

The last city listed in the data set (in row 8602) Wichita Falls

## Question 2

The `listings` variable display the total active listings

## Question 3

```{r}
txhousing <- txhousing |> select(-inventory)

glimpse(txhousing)
```

## Question 4

```{r}
dallas_sub <- txhousing |> filter(city=="Dallas", (year==2012 | year==2013)) 

dallas_sub
```

## Question 5

```{r}
dallas_sub <- dallas_sub |> mutate(prct_sold=sales/listings*100) 

dallas_sub$prct_sold
```

## Question 6

```{r}
dallas_summary <- dallas_sub |> group_by(month) |> summarize(mean_per=mean(prct_sold))

dallas_summary

```

## Question 7

```{r}
  dallas_summary  |> arrange(desc(mean_per)) 

```

## Question 8

The code summarizes all of the steps followed in previous questions: calculate and sort the average percentage of listings that were sold in Dallas from 2012 to 2013

## Question 9

```{r}
txhousing |> filter(month==1, year==2015) |> select(city, listings) |> arrange(listings)

```

San Marcos was the city in January of 2015 that had the fewest houses listed.

## Question 10

```{r}
txhousing |> filter(year==2012) |> group_by(month) |> summarize (summ_sales = sum(sales) ) |> 
 arrange(desc(summ_sales))
```

In August

## Question 11

```{r}
austin_sub <- txhousing |> filter((city=="Austin" | city =="Dallas"), (year==2000 | year==2001)) |> select(sales, city) |> group_by(city) |> summarize(total_sold=sum(sales))

austin_sub
```
